Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2021-09-28 doc/main_jfm.tex
small changes througought

\subsection{Model Parameters}
\cite{Fu20} studied physical quantities for static JP bilayers
for various particle shapes.  In the present study, we fix particle shape and 
vary the background flows.  
Specifically, the
particles are circular disks with diameter $l_0 = 2.5$ nm. The boundary
conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
\theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle center
and director respectively.  The particle diameter is the
thickness of monolayers and the  director points in the
direction of the hydrophobic side of the JP.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tank-Treading Vesicles}
\begin{figure}
\begin{center}
\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
%\hspace{-0.6cm}
%\includegraphics[height=2in]{ReducedArea.pdf}
%\hspace{0.6cm}
%\includegraphics[height=2in]{DecayRate.eps}\\
%\includegraphics[height=2in]{ArcLength.pdf}
%\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4}
 JP vesicles lose enclosed area but conserve length in shear flow. 
  Panel (a) gives the reduced area over time
  for four different shear rates. The monotonic curves are a 
  two-exponential best fit. There is a commensurate increase in excess length (panel (b)), 
  but the arc length of the mid plane curve is more or less constant for all shear rates  (panel (c)).
  The inset in panel (c) is for shear rate 0.003. The legend in panel (b) applies to panels (a)--(c).
  Panel (d) plots the steady-state reduced area and the decay rate $k_2$ (inset) coming from the fitting
  data in panel (a). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
Our simulation studies begin by showing, for the first time, that a JP suspension with hydrophobic attraction 
behaves as a tank-treading vesicle
%with zero viscosity contrast between the fluids inside and
%outside of the vesicle
(\cite{Finken08, Shaqfeh11}).
The centroid of the baseline, $58$-body JP vesicle lies at the origin 
and the background shear flow 
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
\end{align} 
is applied for
shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
and $\mathbf{e}_y$ for the horizontal and vertical directions, respectively.
We use the dimensionless shear rate $\chi = \dot \gamma$ (s$^{-1}$) ns.

\begin{figure}
\begin{center}
\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
\includegraphics[width=11cm]{Figure5B_Wrapper.pdf}
%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
%\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} 
  There is inter-monolayer slip present in the JP vesicle tank-treading motion at all shear rates.  
  Panel (a) tracks a pair of particles (blue and yellow). 
  The shear rate is $\chi=0.005$ and in the right figure, the yellow particle
  will complete two and a quarter revolutions in the same time the blue particle completes two revolutions.
  The curves in panel (b) are the distance the outer leaflet has slid past the inner leaflet. 
  The slopes of the curves gives the slip velocity. 
  With the exception of $\chi = 0.0035$, slip velocity is generally monotonic in the shear rate. }
\end{figure}

Figure~\ref{figure3} shows snapshots of the JP vesicle in the
shear flow with $\chi=0.0025$. 
Under the background flow, the rigid-body boundary condition \eqref{eq:rigid_bc} causes the 
particle suspension to elongate. This perturbation  
disrupts the preferred particle orientations and exposes the hydrophobic core to bulk water (Figure~\ref{figure3}, red region).
In response, hydrophobic attraction \eqref{eq:hydrophobicAttraction} causes the 
particles to reorient and form a  somewhat elliptically-shaped suspension.  
Panels (a) shows the initial configuration and panel (b) shows the later, fully-formed, clockwise tank-treading motion. 
The JP suspension maintains its bilayer structure throughout the simulation. 
%

To extract physical quantities, 
let $A^* = 4\pi A/L^2$ be the reduced area and $\Delta=L/\sqrt{A/\pi}-2\pi$ the excess length of the bilayer
structure (\cite{Finken08}).
Here, $A$ is the enclosed area and $L$ is the total length of the JP vesicle  (Figure \ref{fig:figure0}a).
Figure~\ref{figure4} shows the evolution of the same for various shear rates.
Panels (a) and (b) show that $A^*$ decreases and $\Delta$ increases with time, respectively,
and that the rate of decrease/increase grows with shear rate. 
The total arc length, however, remains constant for all time
for all four shear rates (panel (c)).
We conclude that the JP vesicle loses area and that the bilayer behaves as a permeable membrane.

Since the starting configuration is nearly circular, the reduced area
decreases from an initial value close to $1$ and tends to a steady-state value $A^*_{\infty}$. 
The data in panel (a) are fit by the model 
$A^* = (A^*_{\infty}-a_1-a_2) + a_1 \exp(-k_1t) + a_2 \exp(-k_2t),$ $0 < k_2 < k_1$.
Panel (d) shows that $A^*_{\infty}$ decreases with shear rate. 
The JP vesicle achieves a steady-state reduced area 
earlier when the shear rate is low (inset), but the decay rate $k_2$ is more or less constant for higher shearer rates.

@@

We point out that the range of values for $\chi$ where we measured for tank-treading 
correspond to shear rates $\dot \gamma = O(10^6$ s$^{-1}$) 
which gives fluid velocities O(m s$^{-1}$) in the vicinity of the  vesicle.  
While large, these values are identical to ones used in prior MD studies (\cite{Brandner2019})
and are a consequence of the fact that larger shear rates are required to produce the viscous stresses needed to 
appreciably deform smaller vesicles.

@@

Figure~\ref{figure5}a illustrates the process by tracking the distances traveled 
by a pair of particles. 
In the left image, the blue and yellow particle lie next to each other. 
In the right-most panel, the yellow particle has traveled further than the blue particle. 
This suggests that the tangential velocity of the outer leaflet is larger than that of the inner leaflet.
The difference in their velocities is the slip velocity $U(t)$  and $s(t) = \int_0^t dU $ records the distance
one leaflet has slid past the other.

Figure~\ref{figure5}b plots the sliding distance for various shear rates. 
From the data, we define an inter-monolayer friction coefficient  
\begin{align}
  b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle},
\end{align}
where $F$ is the tangential force jump, $L$ is the length of the midplane $C_M$ (Figure~\ref{figure5}a), $U$ is the slip velocity, and 
$\langle \cdot \rangle$ denotes the time average. 
We define the tangential force jump $F$ to be the tangential shear force on the outer leaflet minus the tangential shear force on the inner leaflet. 
However, it does not make sense to integrate along a curve passing through the particles.  
To calculate the tangential force jump $F$, we instead let 
\begin{equation}
F_h = \int_{\mathcal{C}_M^+} 
    \ttau \cdot \sigma \cdot \nnu \,\dif s -  \int_{\mathcal{C}_M^-} 
    \ttau \cdot \sigma \cdot \nnu \,\dif s 
\end{equation}
where $C_M^+$ and $C_M^-$ are target curves obtained by moving the midplane curve $C_M$ (Figure~\ref{figure5}a)
a distance $h$  outward, respectively inward, along the unit normal.  
We sample $F_h$ for $h = \pm 1.5, \pm 2.5, \pm 3.5$ times the particle radius 
and define $F$ by extrapolating to zero distance.

@@

\subsubsection{Membrane Ruptures}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} 
  Tank-treading leads to membrane rupture for large shear rates.
  }
\end{figure}
A temporary fissure or a complete membrane rupture can occur at large shear
rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture when
suspended in a shear flow. For $\chi = 0.1$, starting
  with a circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
  background flow and fissures appear in the bilayer structure in multiple locations (Figure~\ref{figure8}b). 
  In Figure~\ref{figure8}c, the ruptured vesicles forms two planar micelles which 
  are eventually carried off by the flow (Figure~\ref{figure8}d).

@@

Figure~\ref{figure6} shows four configurations for one specific case
where the centroid of the JP vesicle is initially placed slightly
above the $x$-axis.  We have marked a pair of particles blue and yellow
in the inner and outer leaflets, respectively,  and observe that the 
deformed JP vesicle (Figure~\ref{figure6}, $t = 12~\upmu$s) has a
counterclockwise movement and the shape of the vesicle approaches an
asymmetric slipper shape. For this test, the reduced area in the final
configuration is approximately $0.9$ which matches the previous
numerical tests in~\cite{Kaoui09} where a slipper-like shape occurs when
the flow velocity is weak and the reduced area is large.  The flow causes the 
vesicle, which is initially placed above the axis,
to draft downward where it reaches a steady height of about  $1$ nm.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
%\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle placed in a parabolic flow drifts 
  toward the central axis.  It assumes a slipper shape and undergoes tank-treading
  like in the shear flow case.  The arrows on the left illustrate the background flow and 
  the arrows on the right show the velocity relative to the vesicle's moving frame. 
  The thick black curve plots the distance from the axis as a function of time from left to right.  
  The parameters are $v_{max} = 8$~nm ns$^{-1}$, 
  $w=10$, and $R_0=20$ nm.}
\end{figure}

@@

\subsection{Stretching and Permeability}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
%\includegraphics[height=2in]{relax2.eps}
%\includegraphics[height=2in]{relax.eps}\\
%\includegraphics[height=2.in]{N58_0pres.pdf}
%\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} 
  In JP vesicles, tension and pressure relax as fluid is expelled 
  through the particle interstices. 
  In panel (a), the thin curve plots the mean of the norm of the particle translational velocities.
  The thick curve plots the mean of the absolute value of the particle angular velocities.  
  At $t = 0$ $\upmu$s, the vesicle has a spatially constant internal pressure 0.05~pN nm$^{-1}$ (red color, panel (b)).
  In panel (c),  pressure has dissipated and the vesicle has moved from its initial configuration (gray circles), to the equilibrium configuration
  (black circles).  The data in panels (d) and (e) support the linear relationship expressed by 
  \eqref{eq:LaplacePressure} and \eqref{eq:perm}.
  Circles are for a vesicle with 17 nm initial radius;
  square are for a 34 nm initial radius.  Asterisks are for 
  a 18 nm initial radius but with smaller, 1.25 nm diameter particles. 
  In panel (f), the theoretical time course  \eqref{eq:perm_solution} overlaps the data 
  using constants $K_A$ and $P$ derived from panels (d) and (e). }
\end{figure}
Finally, we show that the JP bilayer behaves as an extensible, permeable membrane. 
Figures~\ref{figure2}b shows an initial, non-equilibrium JP vesicle suspended in a quiescent flow $\uu_{\infty} = 0$.
The color map plots the pressure $p$. The red color in Figures~\ref{figure2}b 
shows a constant, positive internal pressure (0.05~pN nm$^{-1}$)
and the white shows a constant zero, external pressure.  
There is some fluid flow and the pressure vanishes as the configuration tends toward the equilibrium state (Figures~\ref{figure2}c).

What could be the source of this drop in pressure?
In continuum membrane mechanics, changes in surface area give rise to a
membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
membrane surface area and $A_0$ is the reference surface area in the
The area modulus $K_A$ of bilayers is about $240$ pN nm$^{-1}$ (\cite{NaTr00}).
In the two-dimensional vesicles, the tension becomes
\begin{align}
\label{eq:stretch}
\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
\end{align}
where $L$ and $L_0$ are the vesicle arc length and resting length,
respectively. Moreover, stretched, circular vesicles has a Laplace pressure 
\begin{align}
\label{eq:LaplacePressure}
\Delta p = \frac{\tilde \gamma}{R},
\end{align}
where $\Delta p$ is the difference in internal pressure to the pressure
at infinity, $R^{-1}$ is the total curvature of the circular cylinder.

@@

The particles in our setup do not abut but rather have small gaps due to
repulsive forces. The gaps allow for some fluid flux across the JP
bilayer, which can be quantified by the equation
\begin{align}
  \label{eq:perm} 
  \frac{dA}{dt} = -P  L \Delta p,
\end{align}
where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
qua-gan-you2021}).
Figure~\ref{figure2}e shows that the data for 
$L\Delta p$ and $dA/dt$ obey the linear relationship expressed by \eqref{eq:perm}.
The slopes of the linear fits give the hydraulic permeabilities $P = 0.0296$ nm$^3$ ns$^{-1}$
pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 17 nm and 34 nm radius 
cases, respectively.   
Like  the area modulus, permeability is independent of vesicle size.
The hydraulic permeability we calculate, however, is not in agreement with
experimentally derived values and is larger by a few orders of
magnitude.

We suspect this discrepancy is due to inter-particle distance of
the JP being large compared to the inter-lipid spacing in real bilayers. To test this, we calculate the
permeability for the particles with diameter 1.25 nm. 
Due to their smaller size but fixed repulsion strength, these particles have a larger inter-particle spacing 
resulting in an increase in permeability, $P = 0.0566$~nm$^3$~ns$^{-1}$~pN$^{-1}$ (Figure \ref{figure2}e, asterisk symbols).

Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
and~\eqref{eq:perm}, to derive
\begin{align}
\label{eq:perm_solution}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
\end{align}
The theoretical time courses for \eqref{eq:perm_solution} are in good
quantitative agreement with the JP data for
(Figure~\ref{figure2}f).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure9_Wrapper.pdf}
%  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} Two JP vesicles suspended in a shear flow
  interact by orbiting about the origin. The moving paths of the two
  centroids are plotted in blue and red. The centroids are initially
  located on the $x$-axis.  The fluid velocity streamlines appear in grey.
  The dimensionless shear rate is $\chi=0.005$.
  }
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.97\textwidth]{Figure11_Wrapper.pdf}
%\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} 
  The initial placement of two JP vesicles suspended in
  an extensional flow affects the long-time dynamics.  
  The moving paths of the two centroids are plotted
  in blue in red. Each row corresponds to a different initial placement
  of the JP vesicles. 
  (i) Both JP vesicle centroids are on the $x$-axis. (ii) The
  centroid of the left JP vesicle is $0.25$ nm above the $x$-axis
  and the right JP vesicle is on the $x$-axis. (iii) The centroid of
  the left JP vesicle is $0.25$ nm above the $x$-axis and the right
  JP vesicle is $0.25$ units below the $x$-axis. (iv) The centroid of
  the left JP vesicle is $1.25$ nm above the $x$-axis and the
  centroid of the right JP vesicle is $1.25$ nm below the $x$-axis.
  The streamlines appear in grey and 
  the flow rate is $\dot \gamma =0.005$ ns$^{-1}$ in all cases.}
\end{figure}

@@

Figure~\ref{figure12} shows numerical results when the centroids of the
two Janus particles are placed at $(-10,-0.1)$ nm and $(10,0.1)$ nm (case
(iii) from Figure~\ref{figure11}). With this setup, the two JP vesicles
eventually separate along the $\pm y$-directions and we compare the
results against a continuum model as shown in all insets. Panels
(b)--(d) show the transient behavior of the JP vesicles and the
continuum vesicles under an extensional flow. In both the coarse-grained
model and the continuum model, the vesicles initially converge towards
one other and then diverge along the $y$-axis. The behavior of the
streamlines in both cases are similar. The pressure is initially largest
in the gap formed by two JP vesicles and decreases during the
separation. The short-range repulsion plays an important role to avoid
particle collisions.
%and this result can be
%compared with some findings in continuum modeling simulations.

>>>>

\subsection{Model Parameters}
\cite{Fu20} studied physical quantities for static JP vesicles for
various particle shapes. In the present study, we fix the particle shape
and vary the background flows. Specifically, the particles are circular
disks with diameter $l_0 = 2.5$~nm. The boundary
conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
\theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle center
and director respectively. The particle diameter is the thickness of
monolayers and the director points in the direction of the hydrophobic
side of the JP.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tank-Treading Vesicles}
\begin{figure}
\begin{center}
\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
%\hspace{-0.6cm}
%\includegraphics[height=2in]{ReducedArea.pdf}
%\hspace{0.6cm}
%\includegraphics[height=2in]{DecayRate.eps}\\
%\includegraphics[height=2in]{ArcLength.pdf}
%\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4} JP vesicles lose enclosed area but conserve
  length in a shear flow. Panel (a) gives the reduced area over time for
  four different shear rates. The monotonic curves are a two-exponential
  best fit. There is a commensurate increase in excess length (panel
  (b)), but the arc length of the mid plane curve is more or less
  constant for all shear rates (panel (c)). The inset in panel (c) is
  for shear rate 0.003. The legend in panel (b) applies to panels
  (a)--(c). Panel (d) plots the steady-state reduced area and the decay
  rate $k_2$ (inset) coming from the fitting data in panel (a).}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
Our simulation studies begin by showing, for the first time, that a JP
suspension with hydrophobic attraction behaves as a tank-treading
vesicle (\cite{Finken08, Shaqfeh11}). The centroid of the baseline,
$58$-body JP vesicle lies at the origin and the background shear flow 
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
\end{align} 
is applied for shear rate $\dot\gamma$, and orthogonal unit vectors
$\mathbf{e}_x$ and $\mathbf{e}_y$ for the horizontal and vertical
directions, respectively. We use the dimensionless shear rate $\chi =
\dot \gamma$ (s$^{-1}$) ns.

\begin{figure}
\begin{center}
  \includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
  \includegraphics[width=11cm]{Figure5B_Wrapper.pdf}
%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
%\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
\caption{\label{figure5} There is inter-monolayer slip present in the JP
  vesicle tank-treading motion at all shear rates. Panel (a) tracks a
  pair of particles (blue and yellow). The shear rate is $\chi=0.005$
  and in the right figure, the yellow particle will complete two and a
  quarter revolutions in the same time the blue particle completes two
  revolutions. The curves in panel (b) are the distance the outer
  leaflet has slid past the inner leaflet. The slopes of the curves
  gives the slip velocity. With the exception of $\chi = 0.0035$, the
  slip velocity is generally monotonic in the shear rate.}
\end{figure}

Figure~\ref{figure3} shows snapshots of the JP vesicle in the shear flow
with $\chi=0.0025$. Under the background flow, the rigid-body boundary
condition~\eqref{eq:rigid_bc} causes the particle suspension to
elongate. This perturbation disrupts the preferred particle orientations
and exposes the hydrophobic core to bulk water (Figure~\ref{figure3},
red region). In response, hydrophobic
attraction~\eqref{eq:hydrophobicAttraction} causes the particles to
reorient and form a somewhat elliptically-shaped suspension. Panel (a)
shows the initial configuration and panel (b) shows the later,
fully-formed, clockwise tank-treading motion. The JP suspension
maintains its bilayer structure throughout the simulation. 
%

To extract physical quantities, let $A^* = 4\pi A/L^2$ be the reduced
area and $\Delta=L/\sqrt{A/\pi} - 2\pi$ the excess length of the bilayer
structure (\cite{Finken08}). Here, $A$ is the enclosed area and $L$ is
the total length of the JP vesicle (Figure \ref{fig:figure0}a).
Figure~\ref{figure4} shows the evolution of the area and length for
various shear rates. Panels (a) and (b) show that $A^*$ decreases and
$\Delta$ increases with time, respectively, and that the rate of
decrease/increase grows with shear rate. The total arc length, however,
remains constant for all time for all four shear rates (panel (c)). We
conclude that the JP vesicle loses area and that the bilayer behaves as
a permeable membrane.

Since the starting configuration is nearly circular, the reduced area
decreases from an initial value close to $1$ and tends to a steady-state
value $A^*_{\infty}$. The data in panel (a) are fit to the model $A^* =
(A^*_{\infty}-a_1-a_2) + a_1 \exp(-k_1t) + a_2 \exp(-k_2t),$ $0 < k_2 <
k_1$. Panel (d) shows that $A^*_{\infty}$ decreases with the shear rate.
The JP vesicle achieves a steady-state reduced area earlier when the
shear rate is low (inset), but the decay rate $k_2$ is more or less
constant for higher shearer rates.

@@

We point out that the range of values for $\chi$ where we measured for
tank-treading correspond to shear rates $\dot \gamma = \mathcal{O}(10^6$
s$^{-1}$) which gives fluid velocities $\mathcal{O}($m s$^{-1}$$)$ in
the vicinity of the vesicle. While large, these values are identical to
ones used in prior MD studies (\cite{Brandner2019}) and are a
consequence of the fact that larger shear rates are required to produce
the viscous stresses needed to appreciably deform smaller vesicles.

@@

Figure~\ref{figure5}a illustrates the process by tracking the distances
traveled by a pair of particles. In the left image, the blue and yellow
particle lie next to each other. In the right-most panel, the yellow
particle has traveled farther than the blue particle. This suggests that
the tangential velocity of the outer leaflet is larger than that of the
inner leaflet. The difference in their velocities is the slip velocity
$U(t)$ and $s(t) = \int_0^t dU $ records the distance one leaflet has
slid past the other.

Figure~\ref{figure5}b plots the sliding distance for various shear
rates. From the data, we define an inter-monolayer friction coefficient 
\begin{align}
  b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle},
\end{align}
where $F$ is the tangential force jump, $L$ is the length of the
midplane $C_M$ (Figure~\ref{figure5}a), $U$ is the slip velocity, and
$\langle \cdot \rangle$ denotes the time average. We define the
tangential force jump $F$ to be the tangential shear force on the outer
leaflet minus the tangential shear force on the inner leaflet. However,
it does not make sense to integrate along a curve passing through the
particles.  To calculate the tangential force jump $F$, we instead let 
\begin{align}
F_h = \int_{\mathcal{C}_M^+} 
  \ttau \cdot \sigma \cdot \nnu \,\dif s - \int_{\mathcal{C}_M^-} 
 \ttau \cdot \sigma \cdot \nnu \,\dif s 
\end{align}
where $C_M^+$ and $C_M^-$ are target curves obtained by moving the
midplane curve $C_M$ (Figure~\ref{figure5}a) a distance $h$ outward,
respectively inward, along the unit normal. We sample $F_h$ for $h = \pm
1.5, \pm 2.5, \pm 3.5$ times the particle radius and define $F$ by
extrapolating to zero distance.

@@

\subsubsection{Membrane Ruptures}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Tank-treading leads to membrane rupture for
  large shear rates.} 
\end{figure}
A temporary fissure or a complete membrane rupture can occur at large
shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
when suspended in a shear flow. For $\chi = 0.1$, starting with a
circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
background flow and fissures appear in the bilayer structure in multiple
locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
ruptured vesicles form two planar micelles which are eventually carried
off by the flow (Figure~\ref{figure8}d).

@@

Figure~\ref{figure6} shows four configurations for one specific case
where the centroid of the JP vesicle is initially placed slightly above
the $x$-axis. We have marked a pair of particles blue and yellow in the
inner and outer leaflets, respectively, and observe that the deformed JP
vesicle (Figure~\ref{figure6}, $t = 12~\upmu$s) has a counterclockwise
movement and the shape of the vesicle approaches an asymmetric slipper
shape. For this test, the reduced area in the final configuration is
approximately $0.9$ which matches the previous numerical tests
in~\cite{Kaoui09} where a slipper-like shape occurs when the flow
velocity is weak and the reduced area is large. The flow causes the
vesicle, which is initially placed above the axis, to drift downward
where it reaches a steady height of about $1$ nm.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
%\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle placed in a parabolic flow
  drifts toward the central axis. It assumes a slipper shape and
  undergoes tank-treading motion like in the shear flow case. The arrows
  on the left illustrate the background flow and the arrows on the right
  show the velocity relative to the vesicle's moving frame. The thick
  black curve plots the distance from the axis as a function of time
  from left to right. The parameters are $v_{max} = 8$~nm ns$^{-1}$,
  $w=10$, and $R_0=20$ nm.}
\end{figure}

@@

\subsection{Stretching and Permeability}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
%\includegraphics[height=2in]{relax2.eps}
%\includegraphics[height=2in]{relax.eps}\\
%\includegraphics[height=2.in]{N58_0pres.pdf}
%\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} In JP vesicles, tension and pressure relax as
  fluid is expelled through the particle interstices. In panel (a), the
  thin curve plots the mean of the norm of the particle translational
  velocities. The thick curve plots the mean of the absolute value of
  the particle angular velocities. At $t = 0$ $\upmu$s, the vesicle has
  a spatially constant internal pressure 0.05~pN nm$^{-1}$ (red color,
  panel (b)). In panel (c), pressure has dissipated and the vesicle has
  moved from its initial configuration (gray circles), to the
  equilibrium configuration (black circles). The data in panels (d) and
  (e) support the linear relationship expressed by
  \eqref{eq:LaplacePressure} and \eqref{eq:perm}. Circles are for a
  vesicle with 17 nm initial radius; square are for a 34 nm initial
  radius. Asterisks are for a 18 nm initial radius but with smaller,
  1.25 nm diameter particles. In panel (f), the theoretical time course
  \eqref{eq:perm_solution} overlaps the data using constants $K_A$ and
  $P$ derived from panels (d) and (e). }
\end{figure}
Finally, we show that the JP vesicle behaves as an extensible, permeable
membrane. Figures~\ref{figure2}b shows an initial, non-equilibrium JP
vesicle suspended in a quiescent flow $\uu_{\infty} = 0$. The color map
plots the pressure $p$. The red color in Figures~\ref{figure2}b shows a
constant, positive internal pressure (0.05~pN nm$^{-1}$) and the white
shows a constant zero, external pressure. There is some fluid flow and
the pressure vanishes as the configuration tends toward the equilibrium
state (Figures~\ref{figure2}c).

What could be the source of this drop in pressure? In continuum membrane
mechanics, changes in surface area give rise to a membrane tension
$\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the membrane surface area
and $A_0$ is the reference surface area. The area modulus $K_A$ of
bilayers is about $240$ pN nm$^{-1}$ (\cite{NaTr00}). In the
two-dimensional vesicles, the tension becomes
\begin{align}
\label{eq:stretch}
\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
\end{align}
where $L$ and $L_0$ are the vesicle arc length and resting length,
respectively. Moreover, stretched, circular vesicles has a Laplace pressure 
\begin{align}
\label{eq:LaplacePressure}
\Delta p = \frac{\tilde \gamma}{R},
\end{align}
where $\Delta p$ is the difference in internal pressure to the pressure
at infinity and $R^{-1}$ is the total curvature of the circular
cylinder.

@@

The particles in our setup do not abut but rather have small gaps due to
repulsive forces. The gaps allow for some fluid flux across the JP
bilayer, which can be quantified by the equation
\begin{align}
  \label{eq:perm} 
  \frac{dA}{dt} = -P L \Delta p,
\end{align}
where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
qua-gan-you2021}). Figure~\ref{figure2}e shows that the data for
$L\Delta p$ and $dA/dt$ obey the linear relationship expressed by
\eqref{eq:perm}. The slopes of the linear fits give the hydraulic
permeabilities $P = 0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ and $P = 0.0283$
nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 17 nm and 34 nm radius cases,
respectively. Like the area modulus, permeability is independent of
vesicle size.

The hydraulic permeability we calculate, however, is not in agreement
with experimentally derived values and is larger by a few orders of
magnitude. We suspect this discrepancy is due to inter-particle distance
of the JP being large compared to the inter-lipid spacing in real
bilayers. To test this, we calculate the permeability for the particles
with diameter 1.25 nm. Due to their smaller size but fixed repulsion
strength, these particles have a larger inter-particle spacing resulting
in an increase in permeability, $P = 0.0566$~nm$^3$~ns$^{-1}$~pN$^{-1}$
(Figure~\ref{figure2}e, asterisk symbols).

Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
and~\eqref{eq:perm}, to derive
\begin{align}
\label{eq:perm_solution}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
\end{align}
The theoretical time courses for \eqref{eq:perm_solution} are in good
quantitative agreement with the JP data (Figure~\ref{figure2}f).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure9_Wrapper.pdf}
%  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} Two JP vesicles suspended in a shear flow
  interact by orbiting about the origin. The moving paths of the two
  centroids are plotted in blue and red. The centroids are initially
  located on the $x$-axis. The fluid velocity streamlines appear in
  grey.  The dimensionless shear rate is $\chi=0.005$.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.97\textwidth]{Figure11_Wrapper.pdf}
%\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} The initial placement of two JP vesicles
  suspended in an extensional flow affects the long-time dynamics. The
  moving paths of the two centroids are plotted in blue in red. Each row
  corresponds to a different initial placement of the JP vesicles. (i)
  Both JP vesicle centroids are on the $x$-axis. (ii) The centroid of
  the left JP vesicle is $0.25$~nm above the $x$-axis and the right JP
  vesicle is on the $x$-axis. (iii) The centroid of the left JP vesicle
  is $0.25$~nm above the $x$-axis and the right JP vesicle is $0.25$~nm
  below the $x$-axis. (iv) The centroid of the left JP vesicle is
  $1.25$~nm above the $x$-axis and the centroid of the right JP vesicle
  is $1.25$~nm below the $x$-axis. The streamlines appear in grey and
  the flow rate is $\dot \gamma =0.005$~ns$^{-1}$ in all cases.}
\end{figure}

@@

Figure~\ref{figure12} shows numerical results when the centroids of the
two Janus particles are placed at $(-10,-0.1)$~nm and $(10,0.1)$~nm
(case (iii) from Figure~\ref{figure11}). With this setup, the two JP
vesicles eventually separate along the $\pm y$-directions and we compare
the results against a continuum model as shown in all insets. Panels
(b)--(d) show the transient behavior of the JP vesicles and the
continuum vesicles under an extensional flow. In both the coarse-grained
model and the continuum model, the vesicles initially converge towards
one other and then diverge along the $y$-axis. The behavior of the
streamlines in both cases are similar. The pressure is initially largest
in the gap formed by two JP vesicles and decreases during the
separation. The short-range repulsion plays an important role to avoid
particle collisions.
%and this result can be
%compared with some findings in continuum modeling simulations.
